New numerical integration of orbits of irregular satellites and prediction of stellar occultations up to 2020

### 2016-03-14 Irregular-occ/Irregular-occ.tex
.

For the specific case of Phoebe, the ninth satellite of Saturn, we have updated the ephemeris published in \cite{Desmars2013}. The new ephemeris (PH15) used the same dynamical model, including the perturbations of the Sun and the eight planets, the eight major satellites of Saturn and the $J_2$ parameter. The observations used to fit the model are identical to \cite{Desmars2013} (including 223 Cassini observations) with additional observations from \cite{GomesJunior2015}, \cite{Peng2015}, observations from Minor Planet Circulars between 2012 and 2014 (available on the Natural Satellite Data Center\footnote{\url{http://lnfm1.sai.msu.ru/neb/nss/bsapoouf.htm}}), and observations from Flagstaff \citep{NOFS} between 2012 and 2014. It represents a total number of 5886 observations from 1898 to 2014.

@@

For this satellite, we used the most recent ephemeris published by \cite{Emelyanov2015} which is based on more observations than previous ephemeris and covers 4 years more than the ephemeris of \cite{Jacobson2009}. In Fig. \ref{Fig:eph-Triton} we compare it with the ephemeris published in \cite{Zhang2014} and the NEP081 JPL ephemeris \citep{Jacobson2009}. The offsets between the three ephemeris are smaller than 15 mas for the period 2015-2018. This value is much smaller than the apparent size of Triton (124 mas, see Table \ref{Tab: satellite-diameter}), which indicates a good probability of observing an event by this object.

>>>>

For the specific case of Phoebe, the ninth satellite of Saturn, we have updated the ephemeris published in \cite{Desmars2013}. The new ephemeris (PH15) used the same dynamical model, including the perturbations of the Sun and the eight planets, the eight major satellites of Saturn and the $J_2$ parameter. The observations used to fit the model are identical to \cite{Desmars2013} (including 223 Cassini observations) with additional observations from \cite{GomesJunior2015}, \cite{Peng2015}, observations from Minor Planet Circulars between 2012 and 2014 (available on the Natural Satellite Data Center\footnote{\url{http://lnfm1.sai.msu.ru/neb/nss/bsapoouf.htm}}), and observations from Flagstaff \citep{NOFS} between 2012 and 2014. It represents a total number of 5886 observations from 1898 to 2014. In contrast, in \cite{Desmars2013} was used 3367 observations from 1898 to 2012. It represents an increase of almost 75\% in the number of observations.

@@

For this satellite, we used the most recent ephemeris published by \cite{Emelyanov2015} which is based on more observations than previous ephemeris and covers 4 years more than the ephemeris of \cite{Jacobson2009}. In Fig. \ref{Fig:eph-Triton} we compare it with the ephemeris published in \cite{Zhang2014} and the NEP081 JPL ephemeris \citep{Jacobson2009}. The offsets between the three ephemeris are smaller than 20 mas for the period 2015-2021. This value is much smaller than the apparent size of Triton (124 mas, see Table \ref{Tab: satellite-diameter}), which indicates a good probability of observing an event by this object.
